\documentclass[margin]{res}

\usepackage{helvetica}
\textwidth=5.2in
\usepackage{hyperref}
\hypersetup{colorlinks}
\usepackage{color}
\definecolor{darkred}{rgb}{0.4,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\hypersetup{
  colorlinks,
  linkcolor=darkblue,
  filecolor=darkgreen,
  urlcolor=darkred,
  citecolor=darkblue}

\begin{document}

\name{Andrii Mishkovskyi\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf Address} \\ Czaar Peterstraat 103 \\  Amsterdam \\ The Netherlands}

\address{{\bf Contacts} \\ +31 62 980 61 41 \\ contact@mishkovskyi.net \\ \href{https://github.com/mishok13}{GitHub}}

\begin{resume}

% \section{Objective}
% To work on a product which solves real problems, preferrably using reliable and suit-
% able tools. I’d love to work in environment where I can not only contribute, but also
% learn from the team and the products developed.

\section{Education}
BS in Computer Science, NTUU ``Kyiv Politechnical Institute'', 2003 --- 2007

\section{Experience}

{\bf Software Engineer/Team Lead} Screen6 \hfill March 2013 --- present

Cross-device analytics and real-time bidding platform for online
advertisement.

Designed architecture of real-time bidding platform. Designed and
implemented cookie de-duplication platform. Design and implemented the
analytics dashboard. Overlooking development of other projects.

{\bf Core Developer} Hyves \hfill September 2011 --- February 2013

Leading Dutch social network, part of TMG, the largest media company
in Netherlands.

Took part in design and implementation of first Python project at
Hyves, a social login API. Took part in complete overhaul of Speurders
from PHP to Python, second largest classified advertisement site in
Netherlands.

{\bf Senior Software Engineer,} CloudMade \hfill October 2009 --- August 2011\\
{\bf Software Engineer,} CloudMade \hfill August 2008 --- October 2009

Map portal platform providing B2B and B2C services.

Designed and implemented map rendering engine and supporting
distributed machinery. Took part in design of geocoding and routing
services. Heavily contributed to multiple open-source projects used by
the platform.

{\bf Software Engineer,} Visonic Ltd. \hfill July 2007 --- August 2008

Producer of home security and medical hardware and integrated systems.

Maintained desktop applications for managing home security
hardware. Implemented several sub-systems of home security automation
system.

{\bf Tier 2/3 Tech Support,} Telesystems of Ukraine \hfill February 2006 --- July 2007

{\bf System Administrator,} Strum \hfill August 2005 --- February 2006

\section{Skills}
\begin{tabular}{l p{5in}}
  Languages: & Python, Clojure, Emacs Lisp, C \\
  % Libraries: & Cascalog, Guava, Flask, Werkzeug, Apache Commons, Cascading \\
  Tools: & PostgreSQL, Redis, RabbitMQ, Hadoop, GNU Emacs, Docker \\
  % Tools: & GNU Emacs, coreutils, git, Leiningen, fabric, awscli, puppet
\end{tabular}

\section{Talks}

\href{http://lanyrd.com/profile/mishok13/sessions/}{http://lanyrd.com/profile/mishok13/sessions/}

\section{Opensource}

\href{https://github.com/mishok13}{GitHub}\\
\href{https://bitbucket.org/mishok13}{BitBucket}

\end{resume}

\end{document}
